How to select predictive models for decision-making or causal inference?

### 2024-10-03 how_to_select_latex.tex
apd: add effect ratio

We focused on the

@@

\paragraph{Research question needing more work}

@@

TODO

\bibliography{biblio}
%\printbibliography

>>>>

Beyond overlap, we study the effect of varying ratio of causal effect ratio to
baseline on model selection. In our simulation, we vary the empirical mean
absolute difference between the causal effect and the baseline, $\Delta_{\mu} =
    \frac{1}{N} \sum_{i=1}^N \big | \frac{\mu_{1}(x_i) - \mu_{0}(x_i)}{\mu_{0}(x_i)}
    \big|$, covering a range of ratio from 1 to 300. Figure
\ref{fig:effect_ratio_influence} shows that for high values of the ratio,
$R-\text{risk}$ is outperformed by the $\mu\text{-risk}_{IPW}$ and the
$\tau\text{-risk}_{IPW}$. However, on average, the $R-\text{risk}$ is still the
better risk.

@@

\paragraph{Limitations}

@@

Going beyond overlap, we study the effect of another important parameter of the
data generation process: the ratio of causal effect to the baseline response.

For each dataset of our simulation (caussim), we measure it as the absolute mean
difference between the causal effect and the baseline response, measured
empirically on each dataset instance $\Delta_{\mu} = \frac{1}{N} \sum_{i=1}^N
    \big | \frac{\mu_{1}(x_i) - \mu_{0}(x_i)}{\mu_{0}(x_i)} \big|$. We vary a
dedicated parameter ($\omega$ in Algorithm 2) in the simulation to force this
ratio to cover a wide range of values. For 90 dataset instances, it ranges from 1
to 300 with the full distribution of values given in Table \ref{apd:effect_ratio_distribution}.

\begin{table}[!ht]
    \centering
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l|}
        \hline
        ~             & count & mean    & std     & min     & 10\%    & 25\%    & 50\%    & 75\%    & 90\%    & max     \\ \hline
        effect\_ratio & 89    & 99.1291 & 132.525 & 1.24843 & 2.82881 & 4.07361 & 30.1524 & 184.996 & 316.999 & 510.897 \\ \hline
    \end{tabular}
    \caption{Distribution of the causal effect ratio $\Delta_\mu$ for the experiment.}\label{apd:effect_ratio_distribution}
\end{table}

\bibliography{biblio}
